---
title: "57341 Intro to Econometrics"
subtitle: "Problem Set 2"
author: "NathanP23"
output:
  html_document:
    theme: united
    toc: yes
    tod_depth: 3
    toc_float: yes
    df_print: paged
  pdf_document:
    toc: yes
---

```{r setup}
rm(list=ls())         # clean R environment
gc()                  # clean computer memory
options(scipen=999)   # show numbers in normal format

pacman::p_load(       # install if needed and load libraries
  tidyverse,
  haven           # allways call, contains most functions we need
)

my_path <- "/Users/nathan/Documents/HUJI/Introduction to Econometrics/Ex2/"
setwd(my_path) # tell R were on the computer we work
```

# Question 1.

```{r code of Question 1}
# reading csv file
data_bwght <- read.csv("bwght_2022.csv")
# checking the data frame, priniting summary
summary(data_bwght)
```

## A.

```{r code of Question 1.1}
# counting number of lines (each line is a person)
nrow(data_bwght)
# taking length of the id vector excluding values where cigs=0/NA 
length((data_bwght$id[data_bwght$cigs != 0 & !is.na(data_bwght$cigs)]))
```

## B.

```{r code of Question 1.2}
mean(data_bwght$cigs[!is.na(data_bwght$cigs)]) 
```

it is not a good representation because it is including non-smoking ids which are are affected by average. it will be more representative if we use quintiles.

## C.

```{r code of Question 1.3}
sum(data_bwght$cigs[data_bwght$cigs != 0 & !is.na(data_bwght$cigs)]) / length((data_bwght$id[data_bwght$cigs != 0 & !is.na(data_bwght$cigs)]))
```

it id a good indicator because it is only the average on smoking ids without non-smoking ids

## D.

```{r code of Question 1.3}
mean(data_bwght$drink[!is.na(data_bwght$drink)])
```
It is 1554 because we are not counting NA values

# Question 3.

> ```{r code of Question 3}
> # adding row of "police_per_capita" using mutate
> crimes_data <- mutate(crimes_data, police_per_capita = police / pop)
> ```

# Question 4.

> ## A.
>
> > ```{r code of Question 4}
> > # now scattering the graph 
> > ggplot(crimes_data, aes(x = police_per_capita, y = crimes_per_capita)) + geom_point()
> > ```
>
> ## B.
>
> > we see a low linear correlation between crimes and population or police, so this might explain the unknown factor (or error) from question 1 (U)

# Question 5.

> ```{r code of Question 5}
> # taking mean of crimes_per_capita at places where <place> == 1
> mean(crimes_data$crimes_per_capita[crimes_data$west == 1])
> mean(crimes_data$crimes_per_capita[crimes_data$nrtheast == 1])
> mean(crimes_data$crimes_per_capita[crimes_data$south == 1])
> mean(crimes_data$crimes_per_capita[crimes_data$west == 0 & crimes_data$nrtheast == 0 & crimes_data$south == 0])
> # taking mean of police_per_capita at places where <place> == 1
> mean(crimes_data$police_per_capita[crimes_data$west == 1])
> mean(crimes_data$police_per_capita[crimes_data$nrtheast == 1])
> mean(crimes_data$police_per_capita[crimes_data$south == 1])
> mean(crimes_data$police_per_capita[crimes_data$west == 0 & crimes_data$nrtheast == 0 & crimes_data$south == 0])
> ```

# Question 6.

> ## A.
>
> > ```{r code of Question 6}
> > cor(crimes_data$crimes_per_capita,crimes_data$unem)
> > ```
>
> ## B.
>
> > no, there is a slight negative correlation but it is not a causal relation

# Question 7.

> ```{r code of Question 7}
> mean(crimes_data$crimes_per_capita[crimes_data$pop < 350000])
> ```

# Question 8.

> ```{r code of Question 8}
> ggplot(filter(crimes_data,crimes_data$year == 87), aes(x = crimes_per_capita, y = unem)) + geom_point()
> ```

# Question 9.

> there is a correlation between production of planes and cars in the world, but no one is causing the other, so no causal relation.

# Question 10.

> ```{r code of Question 10}
> # data$marri <- ifelse(data$marriedi == 1, 1, 0)
> ```
