---
title: "57341 Intro tor Econometrics B"
subtitle: "Ex3"
author: "NathanP23"
output:
  html_document:
    theme: united
    toc: yes
    tod_depth: 3
    toc_float: yes
    df_print: paged
  pdf_document:
    toc: yes
---

```{r setup}
# This chunk should always appear at the beginning of the PS. You only need to change the path.
rm(list=ls())         # clean R environment
gc()                  # clean computer memory
options(scipen=999)   # show numbers in normal format

pacman::p_load(       # install if needed and load libraries
  tidyverse,
  haven,            # allways call, contains most functions we need
  fixest,           # Regressions
  janitor,          # Clean names and strings
  stringi,           # string edit
  lmtest,
  stargazer
)

my_path <- "/Users/nathan/Documents/HUJI/Introduction to Econometrics/Ex3"
setwd(my_path) # tell R were on the computer we work

```

# Question 1

## a.

```{r}
df <- read.csv("hprices.csv")
centered_price <- df$price - mean(df$price)
centered_sqrft <- df$sqrft - mean(df$sqrft)

```

## b.

### 1)

```{r}
model <- lm(price ~ sqrft, data = df)

summary(model)

coef(model)

cat(paste(
  "The value of b0 is", summary(model)$coefficients[1], 
  "\nThe value of b1 is", summary(model)$coefficients[2],
  "\nThe value of SD(b0) is", summary(model)$coefficients[, "Std. Error"][1],
  "\nThe value of SD(b1) is", summary(model)$coefficients[, "Std. Error"][2],
  "\nThe value of R^2 is", summary(model)$r.squared
  )
)

```

that means that price = 12315.185 + sqrft \* 139.985 + u

### 2)

```{r}
model_centered <- lm(centered_price ~ centered_sqrft, data = df)

summary(model_centered)

coef(model_centered)

cat(paste(
  "The value of b0 is", summary(model_centered)$coefficients[1], 
  "\nThe value of b1 is", summary(model_centered)$coefficients[2],
  "\nThe value of SD(b0) is", summary(model_centered)$coefficients[, "Std. Error"][1],
  "\nThe value of SD(b1) is", summary(model_centered)$coefficients[, "Std. Error"][2],
  "\nThe value of R^2 is", summary(model_centered)$r.squared
  )
)

```

that means that centered_price = 12315.185 + centered_sqrft \* 139.985 + u

## c.

```{r}

plot(df$sqrft, df$price, main = "Linear Regression: Price vs. Square Footage",
     xlab = "Square Footage", ylab = "Price", pch = 19)

abline(model, col = "red")


plot(centered_sqrft, centered_price, main = "Linear Regression: Centered Price vs. Centered Square Footage",
     xlab = "centered_sqrft", ylab = "centered_price", pch = 19)

abline(model, col = "blue")
```

## d.

```{r}
lprice2 <- log(df$price * 1000)
```

### 3.

```{r}
model <- lm(lprice ~ sqrft, data = df)

summary(model)

coef(model)

cat(paste(
  "The value of b0 is", summary(model)$coefficients[1], 
  "\nThe value of b1 is", summary(model)$coefficients[2],
  "\nThe value of SD(b0) is", summary(model)$coefficients[, "Std. Error"][1],
  "\nThe value of SD(b1) is", summary(model)$coefficients[, "Std. Error"][2],
  "\nThe value of R^2 is", summary(model)$r.squared
  )
)
```

that means that lprice = 11.7729203493351 + sqrft \* 0.000387814524583589 + u

### 3.

```{r}
model1 <- lm(lprice2 ~ sqrft, data = df)

summary(model1)

coef(model1)

cat(paste(
  "The value of b0 is", summary(model1)$coefficients[1], 
  "\nThe value of b1 is", summary(model1)$coefficients[2],
  "\nThe value of SD(b0) is", summary(model1)$coefficients[, "Std. Error"][1],
  "\nThe value of SD(b1) is", summary(model1)$coefficients[, "Std. Error"][2],
  "\nThe value of R^2 is", summary(model1)$r.squared
  )
)
```

that means that lprice2 = 11.7729203493351 + sqrft \* 0.000387814524583589 + u

## d.

```{r}

plot(df$sqrft, df$lprice, main = "Linear Regression: lprice vs. Square Footage",
     xlab = "Square Footage", ylab = "lprice", pch = 19)

abline(model, col = "red")


plot(df$sqrft, lprice2, main = "Linear Regression: lprice2 vs. Centered Square Footage",
     xlab = "centered_sqrft", ylab = "lprice2", pch = 19)

abline(model1, col = "blue")
```

When we run a regression with the natural logarithm (log) of the data, we are modeling the relationship on a logarithmic scale. This is often done when the relationship between the variables appears to be nonlinear on the original scale but shows a more linear relationship on the log scale. The coefficients in this case represent the change in the dependent variable for a one-unit change in the independent variable(s) after taking the logarithm. Log-transformation is particularly useful when dealing with data that exhibits exponential growth or decay. It can help linearize the relationship and stabilize variance. However, when we log-transform the data, the interpretation of the coefficients changes. For example, a coefficient of 0.1 on the log scale would imply a multiplicative effect on the original scale (e.g., a 10% change), not an additive change as in the original scale.
